A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-05-19 paper/paper.tex
Compare to clique bound

>>>>

This bound is incomparable to the clique bound, which is given by a greedy
colouring of a microstructure-like graph \citep{DBLP:conf/cp/McCreeshNPS16}.
The clique bound is potentially stronger, in that it can reason about
compatibilities between individual variable-vertex assignments. The clique
bound is also able to make use of edge label information, which CP-FC and our
equivalent bound cannot---this comes at the expense of much higher memory
requirements, and also longer calculation times for unlabelled graphs. The
clique bound is also potentially weaker: it is not even guaranteed to be less
than or equal to the number of remaining variables, in the CP-FC sense.
